### 2019-02-13 1-Preamble/4-Acknowledgement/acknowledgement.tex
Still fighting against my template...
Lots of macro were clean up, almost done for copy/paste of chapter 5 from my ALT 2018 paper

This work is supported by
the French National Research Agency (ANR), under the projects BADASS, SOGREEN and EPHYL (grants \emph{XXX}, \emph{N ANR-14-CE28-0025-02} and \emph{N ANR-16-CE25-0002-03}),
by R\'egion Bretagne, France,
the French Ministry of Higher Education and Research (MENESR),
by \'Ecole Normale Sup\'erieure de Paris-Saclay.
by European Union, through the European Regional Development Fund (ERDF),
and by Ministry of Higher Education and Research, Brittany and Rennes Métropole, through the CPER Project \emph{SOPHIE / STIC \& Ondes}.

@@

% Je souhaite terminer ces remerciements par une pensée toute particulière pour Lola, qui m'a soutenu, qui m'a émerveillé par son enthousiasme et qui m'a réconforté par son amour durant la dernière année. Je t'aime chaton, impressionnant !
Deseo terminar este agradecimiento con un pensamiento especial para Lola, quien me apoyó, me sorprendió con su entusiasmo y me consoló con su amor durante el año pasado.
Yo te quiero gatita, ¡impresivo!

>>>>

This work is supported by
the French National Research Agency (ANR), under the projects BADASS, SOGREEN and EPHYL (grants \emph{N ANR-16-CE40-0002}, \emph{N ANR-14-CE28-0025-02} and \emph{N ANR-16-CE25-0002-03}),
by R\'egion Bretagne, France,
by CNRS under the PEPS project BIO (in $2017$),
by the French Ministry of Higher Education and Research (MENESR),
by \'Ecole Normale Sup\'erieure de Paris-Saclay.
by European Union, through the European Regional Development Fund (ERDF),
and by Ministry of Higher Education and Research, Brittany and Rennes Métropole, through the CPER Project \emph{SOPHIE / STIC \& Ondes}.

@@

% Je souhaite terminer ces remerciements par une pensée toute particulière pour Lola, qui m'a soutenu, qui m'a émerveillé par son enthousiasme et qui m'a réconforté par son amour durant la dernière année. Je t'aime chaton, impressionnant !
Deseo terminar este agradecimiento con un pensamiento especial para Lola, quien me apoyó, me sorprendió con su entusiasmo y me consoló con su amor durante el año pasado.
\textcolor{white}{Yo te quiero gatita, ¡impresivo!}
